Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex

\begin{proof}[Proof of \cref{prop:deg}]
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
\]
\end{proof}

\begin{proof}[Proof of \cref{prop:nds}]
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.

@@

\begin{proof}[Proof of \cref{prop:paths}]
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
\begin{align*}
\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k\leq \\
 &\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
\end{align*}
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
\]
\end{proof}

>>>>

The following proofs have been omitted from the main text. If the reviewers feel they are helpful
and not obvious, we will pay for an extra page to include them.

\bigskip

\propdeg*
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
\]
\end{proof}

\bigskip

\propnds*
\begin{proof}
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.

@@

\bigskip

\proppaths*
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
\begin{align*}
\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
 & \leq \left|\N(t)\cap \N(u)\right|\\
 & \leq \deg(t)
\end{align*}
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
\]
\end{proof}
